### 2022-02-15 manuscript.rmd
Add all files essential for compiling manuscript.rmd; anonymize

keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "7618"

@@

Communication research is often comparative, journalism studies are no exception. For example, comparative approach is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Surveys in journalism research are often comparative, e.g. the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles or behaviours of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.

@@

[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years. One could question the necessity of another repetition in this paper. The non-atomicity argument might be repetitious but we believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p. 356] said-- is still not the default regression approach in communication research. For example, as recent as in 2020 some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. A fallacious result with less error is still fallacious. See also @nezlek:2008:IMM for a criticism of such justification.

@@

Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

@@

Table \@ref(tab:t1) shows a summary of all models from outlet-level analysis using three different ways of modeling. The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$). It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution. By default, *brms* displays the mean and the 95\% high density interval (HDI). [^5] These two values represent the point and interval estimates of the regression coefficient.

[^5]: HDI is one representation of the Bayesian credible interval. It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

@@

We propose several extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes. The analyses in these extensions are not preregistered. Please refer to Appendix I for these extensions.

@@

Regarding the possible "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194) [^loo]. By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not "J shape". In average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 1, Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].

>>>>

keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "8964"

@@

Communication research is often comparative, journalism studies are increasingly so [@hanusch:2019:C]. Comparative approach is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. Around 40% of recent  comparative studies in journalism research are comparative content analysis [@hanusch:2019:C], which include news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Another 10% of recent comparative studies in journalism research are surveys such as the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) or their countries (e.g. post-communist country) influence the content of news articles or behaviors of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.

@@

[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious. We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p. 356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g. an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel]. See also @nezlek:2008:IMM for a criticism of these justifications.

@@

Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

@@

Table \@ref(tab:t1) shows a summary of all models from the outlet-level analysis using three different ways of modeling. The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$). It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution. By default, *brms* displays the mean and the 95\% high density interval (HDI). [^5] These two values represent the point and interval estimates of the regression coefficient.

[^5]: HDI is one representation of the Bayesian credible interval. There should be no "correct" choice of the level of credibility but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\%. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

@@

We propose four extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes. The analyses in these extensions are not preregistered. Please refer to Appendix I for these extensions.

@@

Regarding the possible "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194) [^loo]. By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not "J shape". On average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research. We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models, as Example 2 has shown. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 1, Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6,525 articles in @esser:2013:C or 27,567 journalists in Example 2] can be estimated within a reasonable time frame [^TIME].
